Git Learning Notes

### 2015-01-10 ch-moox/moox.tex
After first review in 2014

The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}. Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}. It is worth mentioning that these parameters are selected and optimized from a wide range of combinations. When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
%growth parameter
\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
\midrule
Typical values  & 800    & 200 & 10 & 10  \\
\bottomrule
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}. The usual length of Si substrate is 1 in. When positioned at 7 in, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

@@

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
% xrd raman
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}
The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}
\end{table}

@@

% sem
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
\caption[SEM imaging on \ce{MoO3} catalytic growth]{SEM imaging on \ce{MoO3} catalytic growth. Effect of alkaline metal-based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts. (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers. Insets show detailed features of different \ce{MoO3} structures.}
\label{fig:ch4sem2by3}
\end{figure}

@@

% tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{MoO3_TEM_XRD.jpg}
\caption[XRD and TEM on \ce{MoO3} catalytic growth]{XRD and TEM on \ce{MoO3} catalytic growth. XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts. (c) Low-magnification TEM image and (d) HRTEM image of nanoplate grown without catalyst. Low-magnification TEM images of (e) forked nanoplate, (f) nanobelt, and (h) microtower, and (g) HRTEM image of nanobelt. Insets show SAED patterns of different \ce{MoO3} 1D structures}
\label{fig:ch4tem3by3}
\end{figure}

@@

Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction. A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}. Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth. A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.

%phase diagram
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{moo3_pdsmall}
\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4} and \ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
\label{fig:ch4pd}
\end{figure}

Based on this phase diagram and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences. First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4(l) + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
%theorem environment

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{vls_mode2}
\caption{Schematic drawing on the growth steps of the proposed growth mode.}
\label{fig:ch4vls}
\end{figure}

@@

\subsection{Growth on Alkaline Metal Containing Substrates}
In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature. This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}. Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica. Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively. Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.

@@

This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates. Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min. And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
% glass growth matrix
\begin{table}[htb]
\centering
\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
\begin{tabular}{lccp{3in}}
\toprule
\multicolumn{3}{c}{Growth Conditions} \\
\cmidrule(l){1-3}
$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
\midrule
700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
700   &  1   & 60  &   irregular shape, not too much growth\\
700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
\bottomrule
\end{tabular}
\end{table}
The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}. These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{moo3_glass}
\caption{Optimized \ce{MoO3} nanoplates growth on glass.}
\label{fig:ch4glass}
\end{figure}

>>>>

The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.\cite{Levin1959} Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}. It is worth mentioning that these parameters are selected and optimized from a wide range of combinations. When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
%growth parameter
\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
\midrule
Typical values  & 800    & 200 & 10 & 10  \\
\bottomrule
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}. The usual length of Si substrate is 1 inch. When positioned at 7 inch, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

@@

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
% xrd raman
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}
The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption[Experimental Raman peaks assignment of \ce{MoO3} on Si]{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM\textsuperscript{\emph{a}}  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}

  \textsuperscript{\emph{a}} R chain mode;

\end{table}

@@

% sem
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
\caption[Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions]{Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts. (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers. Insets show detailed features of different \ce{MoO3} structures.}
\label{fig:ch4sem2by3}
\end{figure}

@@

% tem
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{MoO3_TEM_XRD.jpg}
\caption[XRD and TEM on \ce{MoO3} growths with and without catalyst]{XRD and TEM on \ce{MoO3} growths with and without catalyst. XRD spectra of (a) a specimen grown without catalysts and (b) a specimen grown with NaOH catalysts. (c) Low-magnification TEM image and (d) HRTEM image of nanoplate grown without catalyst. Low-magnification TEM images of (e) forked nanoplate, (f) nanobelt, and (h) microtower, and (g) HRTEM image of nanobelt. Insets show SAED patterns of different \ce{MoO3} 1D structures}
\label{fig:ch4tem3by3}
\end{figure}

@@

Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction. A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}. Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth. A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that\footnote{http://forum.wordreference.com/showthread.php?t=244497} the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.

%phase diagram
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{moo3_pdsmall}
\caption[Phase diagram of \ce{Na2MoO4} and \ce{MoO3}]{Phase diagram of \ce{Na2MoO4}-\ce{MoO3} reproduced from Ref.~\cite{Hoermann1929}}
\label{fig:ch4pd}
\end{figure}

Based on this phase diagram and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences. First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4(l) + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
%theorem environment

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{vls_mode2}
\caption[Schematic drawing on the growth steps of the proposed growth mode]{Schematic drawing on the growth steps of the proposed growth mode.}
\label{fig:ch4vls}
\end{figure}

@@

\subsection{Growth on Alkali Metal Containing Substrates}
In analog with the \ce{Na2MoO4}-\ce{MoO3} binary phase diagram, other alkaline metals, such as Li and K, could also form A-Mo-O alloy at elevated temperature. This fact allows for the usage of a variety of alkaline metal based material as catalyst to promote \gls{vls} or \gls{vss} growth of \ce{MoO3}. Some experiments have been performed in this study, including growth using KI and \ce{Na2CO3} treated Si substrate, glass and mica. Fig.~\ref{fig:ch4al1}a-b show the long belt growth on KI treated Si substrate and towers on ITO glass, respectively. Compared to NaOH-Si growth, the belt on KI appears with rough edge, whereas the towers on ITO glass exhibit stacking features.

@@

This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates. Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min. And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
% glass growth matrix
\begin{table}[htb]
\centering
\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
\begin{tabular}{lccp{3in}}
\toprule
\multicolumn{3}{c}{Growth Conditions} \\
\cmidrule(l){1-3}
$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
\midrule
700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
700   &  1   & 60  &   irregular shape, not too much growth\\
700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
\bottomrule
\end{tabular}
\end{table}
The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}. These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{moo3_glass}
\caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
\label{fig:ch4glass}
\end{figure}
